Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-12 popl24/composition.tex
checkpoint

  \item $\vc{\progtt(\prog,\be_k)}{\itv}{\ttt{"flip[2,gate:g.k]"}}\ \, \text{and} \ \,
    \vc{\progtt(\prog,\be_p)}{\itv}{\ttt{"flip[2,gate:g.p]"}}$
  \item $\vc{\progtt(\prog,\enot\ \be_k)}{\itv}{\ttt{"flip[2,gate:g.k]"}}\ \, \text{and} \ \,
    \vc{\progtt(\prog,\enot\ \be_p)}{\itv}{\ttt{"flip[2,gate:g.p]"}}$

@@

\begin{restatable}[YGC Encode Invariant]{lemma}{ygcencode}
  \label{lemma-ygc-encode}
Given well-typed $\prog_1;E[\mathit{encode}(s_1,s_2)]$ and certified $\mathit{encode}$ where 
$$
\config{\prog_1}{E[\ttt{encode}(s_1,s_2)]} \redxs \config{\prog_1;\prog_2}{E[\ttt{\{wv1=}v_1\ttt{;wv2=}v_2\ttt{\}}]}
$$
If the following preconditions hold where $\iov(\prog_1) = S \cup V$:
\begin{enumerate}
\item $\sep{\progd(\prog_1)}{S_{\{1\}}}{V_{\{2\}}}$
\item $\sep{\progd(\prog_1)}{S_{\{2\}}}{V_{\{1\}}}$
\end{enumerate}
then we have as postconditions where $\iov(\prog_1) = S' \cup V'$:
\begin{enumerate}
\item $\gc{\prog_1;\prog_2}{v_1}{s_1}$ and $\gc{\prog_1}{v_2}{s_2}$
\item $\sep{\progd(\prog_1;\prog_2)}{S'_{\{1\}}}{V'_{\{2\}}}$
\item $\sep{\progd(\prog_1;\prog_2)}{S'_{\{2\}}}{V'_{\{1\}}}$
\end{enumerate}
\end{restatable}

>>>>

  \item $\vc{\progtt(\prog,\be_k)}{\itv}{\ttt{flip[2,"gate:g.k"]}}\ \, \text{and} \ \,
    \vc{\progtt(\prog,\be_p)}{\itv}{\ttt{flip[2,"gate:g.p"]}}$
  \item $\vc{\progtt(\prog,\enot\ \be_k)}{\itv}{\ttt{flip[2,"gate:g.k"]}}\ \, \text{and} \ \,
    \vc{\progtt(\prog,\enot\ \be_p)}{\itv}{\ttt{flip[2,"gate:g.p"]}}$

@@

\begin{restatable}[YGC Encode Invariant]{lemma}{ygcencode}
  \label{lemma-ygc-encode}
Given well-typed $\prog_1;E[\mathit{encode}(s1,s_2)]$ and certified $\mathit{encode}$ where 
%$$
%\config{\prog_1}{E[\mathit{encode}(s_1,s_2)]} \redxs \config{\prog_1;\prog_2}{E[\ttt{\{wv1=}v_1\ttt{;wv2=}v_2\ttt{\}}]}
%$$
If the following preconditions hold where $\iov(\prog_1) = S \cup V$:
\begin{enumerate}
\item $\sep{\progd(\prog_1)}{S_{\{1\}}}{V_{\{2\}}}$
\item $\sep{\progd(\prog_1)}{S_{\{2\}}}{V_{\{1\}}}$
\end{enumerate}
then we have as postconditions where $\iov(\prog_1) = S' \cup V'$:
\begin{enumerate}
\item $\gc{\prog_1;\prog_2}{v_1}{s_1}$ and $\gc{\prog_1}{v_2}{s_2}$
\item $\sep{\progd(\prog_1;\prog_2)}{S'_{\{1\}}}{V'_{\{2\}}}$
\item $\sep{\progd(\prog_1;\prog_2)}{S'_{\{2\}}}{V'_{\{1\}}}$
\end{enumerate}
\end{restatable}
